Generating gaits for physical quadruped robots: evolved neural networks vs. local parameterized search

### 2011-04-13 paper_ecal/fitnessEvaluation.tex
Cleaned a few things up

A separate tracking server, written in Python, ran on the robot and
interfaced with the Wii remote via bluetooth using the CWiid
library\citep{cwiid}.  Our fitness testing code communicated with this
server via a socket connection and requested position updates at the
beginning and end of each run.

@@

The only human intervention required during most learning trials was
to occasionally move the robot back into the viewable area of the Wii
remote.  Initially this was a rare
occurrence, as the gaits did not typically produce motion as large as
the size of the window (roughly 175 x 120 cm).  However, as gaits
improved, particularly when using HyperNEAT, the robot began to walk
out of the measurement area a non-negligible fraction of the time.
Whenever it did so, we would discard the trial and repeat it until the
gait was entirely within the window.

>>>>

A separate tracking server, written in Python, ran on the robot and
interfaced with the Wii remote via bluetooth using the \code{CWiid}
library \citep{cwiid}.  Our fitness testing code communicated with this
server via a socket connection and requested position updates at the
beginning and end of each run.

@@

The only human intervention required during most learning trials was
to occasionally move the robot back into the viewable area of the Wii
remote whenever it wandered outside this window.  Initially this was a rare
occurrence, as the gaits did not typically produce motion as large as
the size of the window (roughly 175 x 120 cm).  However, as gaits
improved, particularly when using HyperNEAT, the robot began to walk
out of the measurement area a non-negligible fraction of the time.
Whenever it did so, we would discard the trial and repeat it until the
gait was entirely within the window.
